%%=============================================================================
%% Voorwoord
%%=============================================================================

\chapter*{\IfLanguageName{dutch}{Woord vooraf}{Preface}}%
\label{ch:voorwoord}

%% TODO:
%% Het voorwoord is het enige deel van de bachelorproef waar je vanuit je
%% eigen standpunt (``ik-vorm'') mag schrijven. Je kan hier bv. motiveren
%% waarom jij het onderwerp wil bespreken.
%% Vergeet ook niet te bedanken wie je geholpen/gesteund/... heeft

As a passionate jump roper, student of applied informatics, I came to the idea of creating an AI skill recognition system based on earlier seen ideas of sign langue detection and emotion recognition. These examples planted a blooming seed which I've proudly grown during my thesis.

I want to thank my promotors Lena De Mol and Thomas Parmentier for the feedback on the paper and the process.
I also want give a big thanks to my co-promotor Dylan Plummer, to aid this Belgian Machine Learning enthiousast into tips and tricks for computer vision, model exploration, concepts and so much more.
I also want to thank Pieter Gibens en Sara De Boever to aid in all my judging questions.
Another special mention is for Gymfed, Eva and Arne, allowing to use earlier competition recordings and for the permission to record freestyles myself from 'behind' the judging table.
I also want to thank Hogent (BIB Lera) for the ability to rent cameras.
During the thesis, I've had a lot of joy in extending my judging knowledge, coding, labeling, training models, inspecting results and creating the Vue3 web app displaying some statistics.

The thesis may have finished, but I've only just begun!